---
title: "Iterations and list columns"
output: github_document
---
```{r}
library(tidyverse)
library(rvest)
library(httr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = 0.6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

## all plots i make will have the viridis color palette
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

```

## Lists
can put anything in a list

```{r}
l = list(
  vec_numeric = 5:8,
  vec_logical = c(TRUE, TRUE, FALSE, TRUE, FALSE, FALSE),
  mat = matrix(1:8, nrow = 2, ncol = 4),
  summary = summary(rnorm(100))
)
```

```{r}
l
l$vec_numeric
l[[1]]
l[["vec_numeric"]][1:3]
mean(l[["vec_numeric"]])

```

## `for` loop

Create a new list 

```{r}
list_norm = 
  list(
    a = rnorm(20, mean = 3, sd = 1),
    b = rnorm(30, mean = 0, sd = 5),
    c = rnorm(40, mean = 10, sd = 0.2),
    d = rnorm(20, mean = 3, sd = 1)
  )
```

```{r}
list_norm
```

Pause and get my old function

```{r}
mean_sd  = function(x) {
  
  if (!is.numeric(x)) {
    stop("Input must be numeric")
  }
  
  if (length(x) < 3) {
    stop("Input must have at least 3 observations")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
  
}
```

I can apply this function to each list element. We have to copy this 4 times.. we can use a for loop instead

```{r}
mean_sd(list_norm[[1]])
mean_sd(list_norm[[2]])
mean_sd(list_norm[[3]])
mean_sd(list_norm[[4]])
```

Let's use a for loop

```{r}
output = vector("list", length = 4)


for (i in 1:4) {

  output[[i]] = mean_sd(list_norm[[i]])

  }
```

Let's try map!

```{r}
output = map(list_norm, mean_sd)
```

What if you want a different function?

```{r}
output = map(list_norm, IQR)
```

```{r}
output = map_dbl(list_norm, median, .id = "input")
```


Binds the output together to a dataframe
```{r}
output = map_df(list_norm, mean_sd, .id = "input")
```


## List columns!! 
keep track of inputs and ouputs at the same time

```{r}
listcol_df = 
  tibble(
    name = c("a", "b", "c", "d"),
    samp = list_norm
  )
```


```{r}
listcol_df %>% pull(name)
listcol_df %>% pull(samp)

listcol_df %>% 
  filter(name == "a")
```



Let's try other operations

```{r}
# apply mean and sd function to the list
mean_sd(listcol_df$samp[[1]])
```

Can I map?
```{r}
#samp is the list column
map(listcol_df$samp, mean_sd)
```


can I add a list column (add output to the list)
In 1 dataframe, we have both input and output information 
```{r}
listcol_df = 
  listcol_df %>% 
  mutate(
    summary = map(samp, mean_sd),
    medians = map_dbl(samp, median))
```









