---
title: "Writing Functions"
output: github_document
---
```{r}
library(tidyverse)
library(rvest)
library(httr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = 0.6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

## all plots i make will have the viridis color palette
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

```

## Do something simple

```{r}
# creating a vector  
x_vec = rnorm(30, mean = 5, sd = 3)

# creating z-score
(x_vec - mean(x_vec)) / sd(x_vec)
```

I want a function that will compute z-scores 
We named input "x" and return "z"

```{r}
z_scores  = function(x) {
  
  z = (x - mean(x)) / sd(x)
  
  return(z)
  
}

## testing function out

z_scores(x_vec)
```


Testing function on other things

```{r error = TRUE}
# can't take mean of character
z_scores("my name is jeff")

# dataset in r (can't take mean of a dataset)
z_scores(mtcars)

# this works because r converts these into numeric (1 and 0)
z_scores(c(TRUE, TRUE, FALSE, TRUE))
```

Update the function so that when people try to use it on something weird, it doesn't work (conditional execution)
if x is not numeric then stop with error statement 
```{r}
z_scores  = function(x) {
  
  if (!is.numeric(x)) {
    stop("Input must be numeric")
  }
  
  z = (x - mean(x)) / sd(x)
  
  return(z)
  
}

```


```{r error = TRUE}
# can't take mean of character
z_scores("my name is jeff")

# Input must be numeric
z_scores(mtcars)

# Input must be numeric
z_scores(c(TRUE, TRUE, FALSE, TRUE))
```

Keep updating 

```{r}
z_scores  = function(x) {
  
  if (!is.numeric(x)) {
    stop("Input must be numeric")
  }
  
  if (length(x) < 3) {
    stop("Input must have at least 3 observations")
  }
  
  z = (x - mean(x)) / sd(x)
  
  return(z)
  
}
```

## Multiple outputs

We want function to spit out mean and SD at the same time

```{r}
mean_sd  = function(x) {
  
  if (!is.numeric(x)) {
    stop("Input must be numeric")
  }
  
  if (length(x) < 3) {
    stop("Input must have at least 3 observations")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
  
}
```

Check that function works

```{r}
x_vec = rnorm(1000)

mean_sd(x_vec)
```

## Multiple Inputs
GIve me an input that spits out the certain output
Create a simulated dataset

I'd like to do the below with a function instead
```{r}
sim_data = 
  tibble(
    x = rnorm(100, mean = 4, sd = 3)
  )


sim_data %>% 
  summarize(
    mean  = mean(x),
    sd = sd(x)
  )
```


trying to create a function
input is the 3 parameters in the tibble above
```{r}
sim_mean_sd = function(samp_size, mu, sigma) {
  
  sim_data = 
  tibble(
    x = rnorm(n = samp_size, mean = mu, sd = sigma)
  )


sim_data %>% 
  summarize(
    mean  = mean(x),
    sd = sd(x)
  )
}


sim_mean_sd(100, 6, 3)

# also can do
sim_mean_sd(samp_size  = 100, mu = 6, sigma = 3)

```


## Reviewing Napoleon Dynamite

```{r, eval = FALSE}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  as.numeric()

review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()

reviews_page1 = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```


What about the next page of reviews... this is tedious to rerun this code 

```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=2"

dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  as.numeric()

review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()

reviews_page2 = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```


Let's turn the code into a function... only thing that changes is the page number

```{r}

read_page_reviews = function(url) {


  html = read_html(url)

  review_titles = 
    html %>%
    html_nodes(".a-text-bold span") %>%
    html_text()

  review_stars = 
    html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("^\\d") %>%
    as.numeric()

  review_text = 
    html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim()

  reviews = tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
)

reviews

}
```

Let's try it out

Can change the url to whatever page you want
```{r}
dynamite_url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=2"

read_page_reviews(dynamite_url)
```


Let's read a few pages of reviews

URL base contains url but no page number
```{r}
dynamite_url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="

dynamite_urls = str_c(dynamite_url_base, 1:5)

# call whatever page you want

all_reiews = 
  bind_rows(
    read_page_reviews(dynamite_urls[1]),
    read_page_reviews(dynamite_urls[2]),
    read_page_reviews(dynamite_urls[3]),
    read_page_reviews(dynamite_urls[4]),
    read_page_reviews(dynamite_urls[5])
)

```



## Mean scoping example

```{r}
f = function(x) {
  
  z = x + y
  z
}

x = 1
y = 2

f(x = y)
```

## Functions as arguements 

```{r}
my_summary = function(x, summ_func) {
  
  summ_func(x)
}

x_vec = rnorm(100, 3, 7)

mean(x_vec)
median(x_vec)

my_summary(x_vec, IQR)
```

